A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-04-29 paper.tex
Added UPre to example in section 3

We construct an interpolant with $F_1 = s(X_T) \land \textsc{treeFormula}(k, T_1)$
and $F_2 = \textsc{treeFormula}(k, T_2)$ (line~5). The only variables shared between $F_1$
and $F_2$ are the state variable copies belonging to node $n$. By the properties of the interpolant,
$F_2 \land \mathcal{I}$ is unsatisfiable, therefore all states in $\mathcal{I}$
are losing against abstract game tree $T_2$ in Figure~\ref{fig:treef2}.  We also know that $F_1 \to
\mathcal{I}$, thus $\mathcal{I}$ contains all states reachable at $n$ by
following $T_1$ and avoiding error states. For example, in the pictured trees
the set $nrequests = 0$ is reachable at $n$ and no move the environment chooses
will reach the error state in one round from this set.

We have discovered a set $\mathcal{I}$ of states losing for the environment.
Environment-losing states are only losing for a particular bound: given that
there does not exist an environment strategy that forces the game into an error
state in $k$ rounds or less; there may still exist a longer environment-winning
strategy.  We therefore record learned environment-losing states along with
associated bounds.  To this end, we maintain a conceptually infinite array of
sets $B^m[k]$ that are may-losing for the controller, indexed by bound $k$.
$B^m[k]$ are initialised to $\top$ for all $k$.  Whenever an environment-losing
set $\mathcal{I}$ is discovered for a node $n$ with bound $\textsc{height}(k,
n)$ in line~13 of Algorithm~\ref{alg:learn}, this set is subtracted from
$B^m[i]$, for all $i$ less than or equal to the bound (lines~14--16).

>>>>

We construct an interpolant with $F_1 = s(X_T) \land \textsc{treeFormula}(k, T_1)$
and $F_2 = \textsc{treeFormula}(k, T_2)$ (line~5). The only variables shared between $F_1$
and $F_2$ are the state variable copies belonging to node $n$. By the properties of the interpolant,
$F_2 \land \mathcal{I}$ is unsatisfiable, therefore all states in $\mathcal{I}$
are losing against abstract game tree $T_2$ in Figure~\ref{fig:treef2}.  We also know that $F_1 \to
\mathcal{I}$, thus $\mathcal{I}$ contains all states reachable at $n$ by
following $T_1$ and avoiding error states.

    In the pictured trees the interpolant $\texttt{nrequests} = 0$ is reachable
    at $n$ and no move the environment chooses will reach an error state in one
    round from this set. A BDD solver using an uncontrollable predecessor
    operation on the error set would be forced to find a much more complicated
    set: $\texttt{nrequests} = 3 \lor (\texttt{nrequests} = 2 \land (
    \texttt{resource0} = 0 \lor \texttt{resource1} = 0)) \lor
    (\texttt{nrequests} = 1 \land (\texttt{resource0} = 0 \land
    \texttt{resource1} = 0))$. This set gets more complicate with more
    resources in the system. The advantage of interpolation is that we may
    overapproximate the losing states.

We have discovered a set $\mathcal{I}$ of states losing for the environment.
Environment-losing states are only losing for a particular bound: given that
there does not exist an environment strategy that forces the game into an error
state in $k$ rounds or less; there may still exist a longer environment-winning
strategy.  We therefore record learned environment-losing states along with
associated bounds.  To this end, we maintain a conceptually infinite array of
sets $B^m[k]$ that are may-losing (\textit{bad}) for the controller, indexed by
bound $k$.  $B^m[k]$ are initialised to $\top$ for all $k$.  Whenever an
environment-losing set $\mathcal{I}$ is discovered for a node $n$ with bound
$\textsc{height}(k, n)$ in line~13 of Algorithm~\ref{alg:learn}, this set is
subtracted from $B^m[i]$, for all $i$ less than or equal to the bound
(lines~14--16).
